I would like to thank professor João do Espírito Santo Batista Neto for the ideas, support, and patience during the development of this work. I also thank professor Odemir Martinez Bruno for the opportunity to work in the bright-field microscopy lab and for the several important remarks and suggestions about the project. I am deeply indebted to professors Moacir Ponti and Marcelo Vieira, whose assistance and guidance were milestones in the completion of this project. \textit{Indeed}, I thank professor Éder Ritis for helping me to develop the mathematical reasoning part of this work and also for the whole-heartedly friendship. My respectful regards to professor Marina Andretta, for sharing your teaching experience and being an extremely supportive and solicitous person. I am also grateful for all USP professors that shared a bit of their broad knowledge. I would like to recognize the invaluable assistance that Isabella de Cassia Lima Munhoz and Marcelo Barbosa de Andrade provided in teaching me how to deal with microscopes.

I owe my deepest gratitude to Ievgeniia Iermak for being by my side during this, supporting my evolution and even helping with optics and microscopy. I acknowledge my parents, who were always there for me since the beginning and offer unconditional support. I am also grateful to all my friends for the irreplaceable good times we had together. No names here just to keep it fair!

I thank Conselho Nacional de Desenvolvimento Científico e Tecnológico - Brasil (CNPq), process 132795/2018-3 for the financial support. This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.